Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Added summary statistics to the appendix.

@tbl-analysis displays the data that is used throughout the analysis and illustrates each of the variables described above. Summary statistics for these variables can be found in the Appendix (SECTION).

@@

# Model

@@

>>>>

@tbl-analysis displays the data that is used throughout the analysis and illustrates each of the variables described above. Summary statistics for these variables can be found in the Appendix (@sec-summary).

@@

# Model {#sec-model}

@@

## Analysis Data Summary Statistics {#sec-summary}

```{r}
#| echo: false
#| message: false
#| label: tbl-summarystats
#| tbl-cap: "Presidential General Election Poll Analysis Data Summary Statistics"

sum_stats <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))

#view(sum_stats)

summary_data <- summary(sum_stats[,c(2,6,10)])
#view(summary_data)

summary_data |>
    kable(
    col.names = c("Numeric Grade", "Sample Size", "pct"),
    digits = 1,
    booktabs = TRUE,
    linesep = "",
    align = c("l", "c", "l"),
    format.args = list(big.mark = ",")
  )

@tbl-summarystats presents the summary statistics for the variables, "Numeric Grade", "Sample Size", and "pct". As the variables "Pollster", "State", "Start Date", "End Date", "Population", "Hypothetical", and "Candidate Name" are classfied as a "character" data type, they are not included in the summary above.

## Model Validation {#sec-validation}
